
\section{Conclusion}
\label{sec:conclusion}
 
This work presents a methodology for measuring turbulence from moored IMU ADVs and details an approach for removing the IMU-measured mooring motion from the ADV's velocity measurements. The IMU integrated into the Nortek Vector ADV has been configured to provide estimates of the ADV's orientation and motion at every time step of the ADV's sampling. The tight integration of the IMU and ADV data streams provides a data set that can be used to correct velocity measurements for mooring motion and rotate those measurements into the Earth's reference frame. 

Comparison of spectra of ADV head motion, $\spec{\uhead}$, to that of motion-corrected, $\spec{\ue}$, and uncorrected spectra, $\spec{\umeas}$, reveals that motion correction improves spectral estimates of moored ADV measurements. In particular, we found that motion-corrected spectra have spectral shapes that are similar to previous measurements of tidal-channel turbulence and have a $f^{-5/3}$ spectral slope at high frequencies. This finding suggests that the motion-corrected spectra resolve the inertial subrange predicted by Kolmogorov's theory of locally isotropic turbulence.

Motion correction reduces motion contamination for all platforms we presented but it does not necessarily remove it completely. This outcome seems to depend on the relative amplitude of platform motion compared to the underlying turbulence being measured. The most notable example of this is from the TTM, which has a large ``swaying" peak at 0.1 Hz. Where this peak is very large---especially in the $v$ component---it is not reduced to a level that is consistent with earlier measurements of tidal-channel turbulence---i.e., there is no smooth roll-off between the low-frequency energy-containing scales and the $f^{-5/3}$ inertial subrange.

This inconsistency indicates that turbulence measurements from moored, motion-corrected IMU ADVs must be interpreted with care. An inspection of spectra presented here suggests that excluding spectral regions where $\spec{\uhead} / \spec{\ue} > 3$ removes persistent-motion contamination peaks while still preserving spectral regions where motion correction is effective. Using this criteria, it is then possible to produce spectral fits that exclude persistent-motion contamination, and provide reliable estimates of turbulence quantities of interest (e.g., $\epsilon$ and $\tke$).

We also discovered that motion correction reduces motion contamination in cross spectra. This finding is important because it suggests that moored IMU-ADV measurements may be used to produce reliable estimates of Reynolds stresses. We utilized these stress estimates and vertical shear estimates, both from the TTM, to estimate $\produz$. 

Finally, we have shown that $\epsilon$ estimates based on motion-corrected spectra scale with the $U^3$, and balance $P_{uz}$ estimates during ebb and flood. Together, these results indicate that bottom boundary layer physics are a dominant process at this site, and that the boundary layer reaches the height of the IMU ADVs (10 m) during ebb and flood. The degree of agreement between $\produz$ and $\epsilon$ also serves as an indicator of the self-consistency of moored IMU-ADV turbulence measurements. 

% * <sheri> 2016-10-24T00:00:00.000Z:
%
% So I have no idea where the "Acknowldegments" section is in the code? We need to add the standard NREL attribution (wherever you choose in this section): "This work was supported by the U.S. Department of Energy under Contract No. DE-AC36-08GO28308 with the National Renewable Energy Laboratory. Funding for the work was provided by the DOE Office of Energy Efficiency and Renewable Energy, Wind and Water Power Technologies Office. second paragraph: "The U.S. Government retains and the publisher, by accepting the article for publication, acknowledges that the U.S. Government retains a nonexclusive, paid-up, irrevocable, worldwide license to publish or reproduce the published form of this work, or allow others to do so, for U.S. Government purposes."


%
% ^.


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "Kilcher_etal_IMU-ADV"
%%% End:
