
\section{Introduction}

Acoustic Doppler velocimeters (ADVs) have been used to make high-precision measurements of water velocity for over 20 years \cite[]{Kraus++1994, Lohrmann++1995}.  Since that time they have been deployed around the world to measure turbulence from a range of platforms, including: stationary structures on ocean- and lake-bottoms, in surface waters from a pole lowered from a ship's bow, in the deep ocean from autonomous underwater vehicles, and on moorings \cite[e.g.][]{Voulgaris+Trowbridge1998, Zhang++2001, Kim++2000, Goodman++2006, Lorke2007, Geyer++2008, Cartwright++2009, Fer+Paskyabi2014}. This work presents ADV turbulence measurements from a tidal channel in Puget Sound that were made from moored and ship-tethered platforms.  Herein we demonstrate a method for utilizing inertial motion sensors to correct the ADV velocity measurements for platform motion (i.e. remove platform motion from the velocity measurements).

%There have also been a range of platforms used to measure turbulence within the ocean using other sensors, such as shear probes, fast-response thermistors, and phase-shift acoustic current meters \citep[]{Doherty++1999, Lueck+Huang1999, Klymak++2003, Moum+Nash2009b, Alford2010}.

%\note{Need to talk about moorings!}

Over the last ten years massive growth in the smart-phone, drone, and `Internet of Things' markets has driven innovation in micro-electrical-mechanical systems (MEMS). One component that has emerged from this sector is the inertial motion unit (IMU), also known as the `Magnetic, angular-rate, gravity' (MARG), or `attitude heading reference system' (AHRS) sensor. These sensors measure three axes of: the earth's magnetic field, angular rotation, and linear acceleration. These signals are then integrated using Kalman filters to estimate the orientation and motion of the sensor \cite[]{Barshan+Whyte1995, Marins++2001, Bachmann++2003}\footnote{Within this literature, `IMU' is generally reserved for a MARG sensor without a magnetometer, but herein we refer to the entire group of sensors that measure motion using accelerometers and angular-rate sensors as `IMU'.}. 

In \note{2010 (when, exactly was this?)}, Nortek began offering a version of their Vector ADV with a Microstrain 3DM-GX3-25 AHRS sensor. Nortek incorporated this IMU sensor's signals into the Vector data stream so that the motion and orientation signals were tightly synchronized with the ADV's velocity measurements. This tight synchronization between the motion and velocity measurements provides a data-stream that can be utilized to quantify ADV motion in the earth's inertial reference frame, and remove that motion from the ADV's velocity measurements at each time-step of the ADV's sampling.

This work was motivated by a need for high-precision, low-cost measurements of turbulence at tidal energy sites at the hub-height of typical tidal energy devices.  Experience in the wind energy industry has shown that wind turbine lifetime is strongly influenced by details of atmospheric turbulence, and the same is expected to be true for tidal energy turbines \cite[]{Hand++2003, Kelley++2005, Mucke++2011, Afgan++2013, Mccaffrey++2015, Alexander+Hamlington2015}.  Moored ADVs were identified as a relatively low-cost approach to measuring the turbulence at the scales of interest for tidal device engineering (i.e. length scales between the blade-cord length and the rotor diameter). However, the motion of these platforms is known to contaminate the measurements, and so the IMU-equipped ADV provides an opportunity to remove that motion from the measurements.

Acoustic Doppler profilers (ADPs) provide adequate measurements of the mean flow, but the beam spread of these measurements means that they do not resolve the scales of interest. Acoustic Doppler velocimeters, on the other hand, provide sufficient accuracy, but most measurements using these sensors are from fixed platforms. 

it is necessary to position a sufficiently precise velocity sensor, such as an ADV, at the hub-height of tidal energy turbine (i.e. $>5$ meters above the bottom). 
Remote measurements of velocity with acoustic Doppler profilers (ADPs) , but the measurements from these tools are implicitly averaged over spatial scales (i.e. due to beam-spread) that are larger than the scales of interest for tidal energy device engineering (i.e. ). This presents the challenge of either positioning the ADV on a fixed structure, or of utilizing a moving structure such as a mooring or 


Based on this, This limitation encourages the use of higher precision velocity sensors, such as an ADV. These sensors, however, must be positioned at the exact location  at the hub-height of the tidal energy device.  location of the 

ADVs are There have been some  studies that utilize spatially fixed ADVs to measure 

On the other to tidal energy devices have broad spatial  issues do not have the same level of accuracy as -low accurac estimates of instruments tidal energy measuring turbulence at the hub-heights of tidal energy devices

showed that Earlier Acoustic approach substantially improves the accuracy and precision of moored 

a level of accuracy in mor

This work details a methodology for measuring hub height inflow turbulence using moored acoustic Doppler velocimiters (ADVs). This approach is motivated by the shortcomings of alternatives. For example, remote velocity measurements (i.e., from acoustic Doppler profilers) lack sufficient precision for device simulation, and rigid tower-mounted measurements are very expensive and technically challenging in the tidal environment. Moorings offer a low-cost, site-adaptable and robust deployment platform, and ADVs provide the necessary precision to accurately quantify turbulence.

The primary concern of this approach is that mooring motion will contaminate velocity measurements and reduce their accuracy. Here we demonstrate that  measurements of mooring motion from inertial sensors can be used to correct this motion contamination.  This makes mooring-based velocity measurements a sufficiently precise, low-cost and robust approach for measuring turbulent inflow at hydrokinetic turbine sites.


Acoustic Doppler profilers (ADPs) have 

This provides a level of turbulence-measurement precision that 

An important detail of these methods is that the integration step tends to amplify small low-frequency bias-errors in the accelerometer and angular-rate measurements. The Kalman filtering utilizes the magnetometer measurements of the earth's magnetic field to provide an independent reference vector in the earth's coordinate system, and the accelerometer measurements of gravity provide a second reference vector. These vectors are used to stabilize orientation estimates in the earth's reference frame that would otherwise drift wildly due to the bias-errors \cite[]{Haid+Breitenbach2004, Madgwick++2011}. This approach effectively stabilizes orientation estimates, but velocity estimates based on integration of the accelerometers is still subject to the low-frequency bias errors.

 the ADV's This orientation, acceleration and angular-rate measurements from this IMU sensor were sampled from the 
This work presents the details of 
Details of utilizing accelerometers f Care must therefore be taken when estimating velocity or position from the accelerometers. Careful attention to these errors must be considered when interpreting the 

These errors can be corrected by a stable estimate of velocity or position, or the velocity estimates derived from the IMU measurements must be interpreted with careful attention to the errors  On the ocean surface, GPS is increasingly being employed to provide  is a frequently employed to low-frequency measurement of sensor motion or position is needed to c

that would be contaminated by  co correct for small biases in the angular stabilize the orientation estimates and correct for  provide an independent estimate of  stable estimate of the direction of the earth's magnetic field, are used to stabilize these errors by providing a low-frequencyso that the orientation measurements are stable and converge the provide  the are utilized to 

 provide an independent   is that These methods utilize the accelerometer signal to estimate the direction of the earth's gravity (i.e. down), and the magnetometer provides an estimate of the  ,these methods utilize the rate sensors with the accelerometers and 

IMUs have been used in the aerospace and aeronautical industries for several decades, but their cost has come down as their market has grown beyond these niche sectors \cite[]{Bevly2004}.

Several works have utilized IMUs into oceanographic measurements for characterizing motion of the measurement platform

% The massive growth in the smartphone and drone markets over the last 10 years, and the birth of the `Internet of Things', is helping to drive growth in .  , their has been a rapid explosion of decades inertial sensors have 
% Inertial motion units (IMUs) are sensors that measure three axes of linear acceleration and three axes of angular rotation, thus providing an estimate of all six degrees of freedom of their motion. Because these sensors measure rates of rotation and velocity, they must be integrated to estimate orientation and velocity \cite[]{Barshan+Whyte1995}. During this integration step small bias-errors in the signals can grow dramatically to contaminate estimates of velocity and orientation.  Their is a large body of work devoted  wealth of accelerometer or rate  are also frequently equipped Additionally, several and are equipped with a micro-processor that  measure the 6-axis motion of 
% have been used 

Vertical micro-structure profilers, equipped with highly-sensitive shear probes, have been used throughout the world's oceans to measure turbulence velocity fluctuations. 



\cite[]{Winkel++1996} has one of the first `multi-scale profilers' that quantified platform motion to estimate total velocity profile.

\cite[]{Stahr+Sanford1999} used electromagnetic velocity measurements, with an ADCP that tracked the bottom to estimate the `mean offset'. 

\cite[]{Hayes++1984} also used EM measurements(??), with calculations for body orientation changes.

\cite{Lueck++2002} has a good review of turbulence measurements. 

There has been some effort to characterize and quantify platform motion 

\cite{Miller++2008} performed motion-correction of sonic anemometer data.

Need to cite \cite[]{Paskyabi+Fer2013}: they use a StableMoor, with shear probes. They do have an IMU ``Gyrocube 3F'' built into their MicroRider, but they did not appear to perform motion correction.

\cite[]{Lueck+Huang1999} measured turbulence from a large straemlined-buoy on mooring with shear probes. \cite[]{Klymak++2003} measured turbulence at Hawaiian ridge using towed streamlined body, with shear probes. \cite[]{Moum+Nash2009b}: measuring turbulence from moorings (temperature variance $\chi$-pods).

\cite[]{Doherty++1999} `moored profiler' uses acoustic current meters (`phase shift'/travel-time, not Doppler). \cite[]{Nash++2004, Alford2010}.

Any reason to cite \cite{Williams1996}'s velocity measurement review paper?

\begin{itemize}
\item Brief history of ADVs
\item Discussion of ADV v. ADP measurement
\item ADVs have been difficult to deploy at mid-depths
\item Availability of cheap+accurate IMUs (from smartphone tech) facilitates a new era of ADV measurement from moored platforms.
\item Emphasize noise issue and spatial smearing of ADPs.
\item Reference to `Part 1'.
\item This work developed for MHK, but has wider applications.
\end{itemize}



%%% Local Variables:
%%% mode: latex
%%% TeX-master: "Kilcher_etal_IMU-ADV"
%%% End:
